### 2020-02-12 paper1/article.tex
DLCD -> HLGD. Re-read Chp 2,3. Briefly paper 7.

%In the end, 
\Ge{After correcting the level set on a $2\epsilon$ band around the interface, a reinitialization step is required to redistance the values within the entire narrow band ($2\gamma$).} The two procedures can be readily combined, since it is not necessary to perform mass correction at every time step. Also, because the formalism is cast in a level set frame, generalization from 2D to 3D is trivial. \Ge{Comparing with other mass-preserving methods, the additional computational cost of ICLS is small. This is due to the simple algebraic expression of ${\bm u}_c$ (Eq.\ \eqref{correction vel sol *}), and only one solve of Eq.\ \eqref{inflation} is required}; whereas a typical VOF-coupling method involves solving another set of transport equations \citep{Sussman_JCP_2000}, or reconstructing the interface by an iterative procedure \citep{Luo_JCP_2015}.

@@

\Ge{As introduced earlier, colloidal droplets transported in microfluidic devices are subject to various forces, a typical of which is the depletion force. The depletion force arises from the exclusion of the surfactant micelles in the colloidal suspension. It is often characterized as a near-field attracting potential \citep{Asakura_1958, Mewis_colloidal}, and plays a key role in the droplet dynamics \citep{Shen_AS_2016, Shen_thesis}.}
 Below, we first provide a brief background on the colloidal theory of the depletion potential, then present a numerical model to enforce the depletion force using MLS and GFM.

@@

\Ge{%The preceding model for the depletion force is written in 1D because of symmetry. In practice, droplets may deform due to other external forces and it is not always possible to define a symmetry axis. 
Provided a hydrodynamic model for the depletion force between two droplets, we can easily generalize it to multiple droplets using the MLS.
Thanks to the distance information embedded in the level set functions, it is straightforward to identify the overlap region of arbitrary geometries. Furthermore, as the jump of the osmotic pressure occurs only across the overlap shell, we can define
\begin{equation}
    [p']_\Omega = p'(r'/r_s) - p'(1),
    \label{pot P jump}
\end{equation}
similar to the Laplace pressure jump $[p]_\Gamma$ implemented by the GFM. Based on these observations, we propose a numerical method to compute the depletion force as laid out in Algorithm \ref{al: depletion}.}

>>>>

%In the end, 
\Ge{After correcting the level set on a $2\epsilon$ band around the interface, a reinitialization step is required to redistance the values within the entire narrow band ($2\gamma$).} The two procedures can be readily combined, since it is not necessary to perform mass correction at every time step. Also, because the formalism is cast in a level set frame, generalisation from 2D to 3D is trivial. \Ge{Comparing with other mass-preserving methods, the additional computational cost of ICLS is small. This is due to the simple algebraic expression of ${\bm u}_c$ (Eq.\ \eqref{correction vel sol *}), and only one solve of Eq.\ \eqref{inflation} is required}; whereas a typical VOF-coupling method involves solving another set of transport equations \citep{Sussman_JCP_2000}, or reconstructing the interface by an iterative procedure \citep{Luo_JCP_2015}.

@@

\Ge{As introduced earlier, colloidal droplets transported in microfluidic devices are subject to various forces, a typical of which is the depletion force. The depletion force arises from the exclusion of the surfactant micelles in the colloidal suspension. It is often characterised as a near-field attracting potential \citep{Asakura_1958, Mewis_colloidal}, and plays a key role in the droplet dynamics \citep{Shen_AS_2016, Shen_thesis}.}
 Below, we first provide a brief background on the colloidal theory of the depletion potential, then present a numerical model to enforce the depletion force using MLS and GFM.

@@

\Ge{%The preceding model for the depletion force is written in 1D because of symmetry. In practice, droplets may deform due to other external forces and it is not always possible to define a symmetry axis. 
Provided a hydrodynamic model for the depletion force between two droplets, we can easily generalise it to multiple droplets using the MLS.
Thanks to the distance information embedded in the level set functions, it is straightforward to identify the overlap region of arbitrary geometries. Furthermore, as the jump of the osmotic pressure occurs only across the overlap shell, we can define
\begin{equation}
    [p']_\Omega = p'(r'/r_s) - p'(1),
    \label{pot P jump}
\end{equation}
similar to the Laplace pressure jump $[p]_\Gamma$ implemented by the GFM. Based on these observations, we propose a numerical method to compute the depletion force as laid out in Algorithm \ref{al: depletion}.}

### 2020-02-12 paper2/article.tex
DLCD -> HLGD. Re-read Chp 2,3. Briefly paper 7.

So far, we have showed i) the self-assembly of two to ten droplets in quiescent flows, ii) the alignment of a droplet pair in confined simple shear flows, and iii) the chaining (or, sometimes clustering) of a triplet in the Poiseuille flow. Of these, i) is caused solely by the near-field depletion force, and provides the necessary condition for ii) and iii); ii) and iii) are closely related, and in principle can be generalized to clusters of $N>3$. In addition, we have distinguished our $3D$ channel from typical $q2D$ ones. The remaining question is what makes the droplets self-assemble into compact clusters within short distances (i.e.\ $\sim \mathcal{O}(10D)$ \footnote[4]{Dipolar interactions under similar confinement require at least $\mathcal{O}(100D)$ distance to see any clustering effect, see \cite{Fouxon_2017}.}) as seen in the experiment of   \cite{Shen_2016AS}?

>>>>

So far, we have showed i) the self-assembly of two to ten droplets in quiescent flows, ii) the alignment of a droplet pair in confined simple shear flows, and iii) the chaining (or, sometimes clustering) of a triplet in the Poiseuille flow. Of these, i) is caused solely by the near-field depletion force, and provides the necessary condition for ii) and iii); ii) and iii) are closely related, and in principle can be generalised to clusters of $N>3$. In addition, we have distinguished our $3D$ channel from typical $q2D$ ones. The remaining question is what makes the droplets self-assemble into compact clusters within short distances (i.e.\ $\sim \mathcal{O}(10D)$ \footnote[4]{Dipolar interactions under similar confinement require at least $\mathcal{O}(100D)$ distance to see any clustering effect, see \cite{Fouxon_2017}.}) as seen in the experiment of   \cite{Shen_2016AS}?

### 2020-02-12 paper3/article.tex
DLCD -> HLGD. Re-read Chp 2,3. Briefly paper 7.

The undisturbed flow $\bm u^0$, in the absence of  particles, is the Poiseuille flow driven by the constant pressure gradient $\nabla p^0$,
\begin{eqnarray}&&
u^0_x=\frac{z(z-h)\nabla_x p^0}{2\eta},\ \ \nabla p^0=\eta\nabla^2\bm u^0.\label{ps}
\end{eqnarray}
where $\eta$ is the fluid viscosity, $z$ is the vertical coordinate and $h$ is the channel width. The flow is in $x-$direction, $\nabla_x p^0=-|\nabla_x p^0| \bm{\hat x}$. In the presence of a freely suspended particle we look for the solution of,
\begin{eqnarray}&&%\!\!\!\!\!\!\!\!\!\!\!\!\!
\nabla p=\eta\nabla^2\bm u,\ \ \nabla\cdot\bm u=0,\ \ \ \ \bm u(z=0)=\bm u(z=h)=0,\nonumber\\&&%\!\!\!\!\!\!\!\!\!\!\!\!\!
u_x(\infty)=\frac{z(z-h)\nabla_x p^0}{2\eta},
\label{ds}
\end{eqnarray}
which holds outside the particle. The flow is completely determined when solving for the particle motion, i.e.\ knowing the instantaneous particle position as it determines the boundary condition $\bm u_{S}(\bm x)$ on the 
 particle surface $S$. In the case of a rigid particle, $\bm u_{S}(\bm x)=\bm v+\bm \omega\times (\bm x-\bm y)$ where $\bm v$ and $
\bm \omega$ are the particle translational and angular velocities  and $\bm y=(x_p, y_p, z_p)$ is the coordinate of the particle center of mass. The velocities $\bm v$ and $\bm \omega$ are determined by the solution of the equation for the particle motion coupled with the flow. These velocities could be time-independent as in the case of the steady motion of a neutrally buoyant rigid particle or the case of a non-neutrally buoyant particle after sedimentation when reaching the bottom wall (the theoretical determination of these velocities is impossible generally because of the interaction with the walls). These velocities can also be time-dependent as in the case of
a transient flow  or the gravitational settling of a non-neutrally buoyant particle. If several particles are considered, a time-dependent configuration can be induced by their interactions. We assume here that the time variations are not fast so that the unsteady time-derivative term of the Navier-Stokes equations is negligible (for the steady motion of one particle the time-derivative is the spatial derivative of the flow along the streamline which is small  because of the smallness of the Reynolds number). In the case of droplets the boundary condition on the surface is determined by matching with the inner flow. However there is no need for solving for this inner flow since the detailed form of $\bm u_{S}(\bm x)$ is irrelevant for the derivation of the present representation. The generalization of the problem to the case of many particles is obvious.

@@

%We can describe clearly the far flow of the particle introducing the effective radius $a_0$ by $\tilde {\bm d}=a_0^2\bm v$. Here $\bm v=-v{\hat x}$ is the velocity of the particle in the frame that moves with velocity
%$-h^2 \nabla p^0/(12\eta)$. We have $v>0$ since the particle moves slower than the fluid, cf. Eq.~(\ref{dl}). We find,
%\begin{eqnarray}&&
%a_0^2=\frac{s}{4\pi v \eta   h}.
%\end{eqnarray}
%Thus we can characterize different geometries of the sphere location in the channel, as described by $z_p$ and the radius $a$ of the sphere, using the dimensionless ratio $a_0^2/a^2=s/(4\pi v \eta  a^2 h)$.

@@

%\section{Pair exchange}
This characterizes the basic property of the interaction given by Eq.~(\ref{ints}), that the velocity induced by particle $i$ at the position of the $k-$th particle is equal to the velocity induced by particle $k$ at the position of the $i-$th particle. Thus the interparticle distances can change only if there are three or more particles. We can re-write the equation of motion as
\begin{eqnarray}&&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
\frac{d\bm r_{ik}}{dt}=\sum_{l\neq i, l\neq k}\left(\frac{q}{r_{il}^2}\left[\bm {\hat x}\!-\!\frac{2 \left(\bm r_{il}\cdot\bm {\hat x}\right) \bm r_{il}}{r_{il}^2}\right]\right.\nonumber\\&&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\left.-\frac{q}{r_{kl}^2}\left[\bm {\hat x}\!-\!\frac{2 \left(\bm r_{kl}\cdot\bm {\hat x}\right) \bm r_{kl}}{r_{kl}^2}\right]\right).
\end{eqnarray}
We start by considering in more detail the simplest case of two particles whose distance is constant in time. If the particles have the same $y-$coordinate then the $x-$coordinates obey,
\begin{eqnarray}&&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
\frac{dx_1}{dt}=\frac{dx_2}{dt}=-\frac{q}{(x_1-x_2)^2}.
\end{eqnarray}
In this case the particles form a simple cluster with fixed distance that  moves as a whole slower than the particles separately. We consider now two particles at different spanwise locations, $y_1=y$, $y_2=0$,
\begin{eqnarray}&&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
\frac{dx_1}{dt}=\frac{dx_2}{dt}=\!q\frac{(y_1-y_2)^2-(x_1-x_2)^2}{\left[(x_1-x_2)^2+(y_1-y_2)^2\right]^2},\nonumber\\&&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
\frac{dy_1}{dt}=\frac{dy_2}{dt}\!=\!-q\frac{2(x_1-x_2)(y_1-y_2)}{\left[(x_1-x_2)^2+(y_1-y_2)^2\right]^2}.
\end{eqnarray}
The RHSs are constant because inter-particle distances are but the velocity of the cluster of the two particles can change sign unlike the previous case. For two particles with the same $x$ coordinate, the $x-$ component of their velocity increases while the $y-$component is zero, see \cite{tab0} for experimental observations.

>>>>

The undisturbed flow $\bm u^0$, in the absence of  particles, is the Poiseuille flow driven by the constant pressure gradient $\nabla p^0$,
\begin{eqnarray}&&
u^0_x=\frac{z(z-h)\nabla_x p^0}{2\eta},\ \ \nabla p^0=\eta\nabla^2\bm u^0.\label{ps}
\end{eqnarray}
where $\eta$ is the fluid viscosity, $z$ is the vertical coordinate and $h$ is the channel width. The flow is in $x-$direction, $\nabla_x p^0=-|\nabla_x p^0| \bm{\hat x}$. In the presence of a freely suspended particle we look for the solution of,
\begin{eqnarray}&&%\!\!\!\!\!\!\!\!\!\!\!\!\!
\nabla p=\eta\nabla^2\bm u,\ \ \nabla\cdot\bm u=0,\ \ \ \ \bm u(z=0)=\bm u(z=h)=0,\nonumber\\&&%\!\!\!\!\!\!\!\!\!\!\!\!\!
u_x(\infty)=\frac{z(z-h)\nabla_x p^0}{2\eta},
\label{ds}
\end{eqnarray}
which holds outside the particle. The flow is completely determined when solving for the particle motion, i.e.\ knowing the instantaneous particle position as it determines the boundary condition $\bm u_{S}(\bm x)$ on the 
 particle surface $S$. In the case of a rigid particle, $\bm u_{S}(\bm x)=\bm v+\bm \omega\times (\bm x-\bm y)$ where $\bm v$ and $
\bm \omega$ are the particle translational and angular velocities  and $\bm y=(x_p, y_p, z_p)$ is the coordinate of the particle center of mass. The velocities $\bm v$ and $\bm \omega$ are determined by the solution of the equation for the particle motion coupled with the flow. These velocities could be time-independent as in the case of the steady motion of a neutrally buoyant rigid particle or the case of a non-neutrally buoyant particle after sedimentation when reaching the bottom wall (the theoretical determination of these velocities is impossible generally because of the interaction with the walls). These velocities can also be time-dependent as in the case of
a transient flow  or the gravitational settling of a non-neutrally buoyant particle. If several particles are considered, a time-dependent configuration can be induced by their interactions. We assume here that the time variations are not fast so that the unsteady time-derivative term of the Navier-Stokes equations is negligible (for the steady motion of one particle the time-derivative is the spatial derivative of the flow along the streamline which is small  because of the smallness of the Reynolds number). In the case of droplets the boundary condition on the surface is determined by matching with the inner flow. However there is no need for solving for this inner flow since the detailed form of $\bm u_{S}(\bm x)$ is irrelevant for the derivation of the present representation. The generalisation of the problem to the case of many particles is obvious.

@@

%We can describe clearly the far flow of the particle introducing the effective radius $a_0$ by $\tilde {\bm d}=a_0^2\bm v$. Here $\bm v=-v{\hat x}$ is the velocity of the particle in the frame that moves with velocity
%$-h^2 \nabla p^0/(12\eta)$. We have $v>0$ since the particle moves slower than the fluid, cf. Eq.~(\ref{dl}). We find,
%\begin{eqnarray}&&
%a_0^2=\frac{s}{4\pi v \eta   h}.
%\end{eqnarray}
%Thus we can characterise different geometries of the sphere location in the channel, as described by $z_p$ and the radius $a$ of the sphere, using the dimensionless ratio $a_0^2/a^2=s/(4\pi v \eta  a^2 h)$.

@@

%\section{Pair exchange}
This characterises the basic property of the interaction given by Eq.~(\ref{ints}), that the velocity induced by particle $i$ at the position of the $k-$th particle is equal to the velocity induced by particle $k$ at the position of the $i-$th particle. Thus the interparticle distances can change only if there are three or more particles. We can re-write the equation of motion as
\begin{eqnarray}&&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
\frac{d\bm r_{ik}}{dt}=\sum_{l\neq i, l\neq k}\left(\frac{q}{r_{il}^2}\left[\bm {\hat x}\!-\!\frac{2 \left(\bm r_{il}\cdot\bm {\hat x}\right) \bm r_{il}}{r_{il}^2}\right]\right.\nonumber\\&&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\left.-\frac{q}{r_{kl}^2}\left[\bm {\hat x}\!-\!\frac{2 \left(\bm r_{kl}\cdot\bm {\hat x}\right) \bm r_{kl}}{r_{kl}^2}\right]\right).
\end{eqnarray}
We start by considering in more detail the simplest case of two particles whose distance is constant in time. If the particles have the same $y-$coordinate then the $x-$coordinates obey,
\begin{eqnarray}&&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
\frac{dx_1}{dt}=\frac{dx_2}{dt}=-\frac{q}{(x_1-x_2)^2}.
\end{eqnarray}
In this case the particles form a simple cluster with fixed distance that  moves as a whole slower than the particles separately. We consider now two particles at different spanwise locations, $y_1=y$, $y_2=0$,
\begin{eqnarray}&&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
\frac{dx_1}{dt}=\frac{dx_2}{dt}=\!q\frac{(y_1-y_2)^2-(x_1-x_2)^2}{\left[(x_1-x_2)^2+(y_1-y_2)^2\right]^2},\nonumber\\&&\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
\frac{dy_1}{dt}=\frac{dy_2}{dt}\!=\!-q\frac{2(x_1-x_2)(y_1-y_2)}{\left[(x_1-x_2)^2+(y_1-y_2)^2\right]^2}.
\end{eqnarray}
The RHSs are constant because inter-particle distances are but the velocity of the cluster of the two particles can change sign unlike the previous case. For two particles with the same $x$ coordinate, the $x-$ component of their velocity increases while the $y-$component is zero, see \cite{tab0} for experimental observations.
